---
title: "Example of Analysis"
author: "Panfeng Liang"
date: "June 22, 2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r include=FALSE}
#library(readxl)
#library(ggplot2)
library(dplyr)
clean.data=read.csv("data.csv")
attach(clean.data)
```

## Analysis of Death Rate through Logistic Model :

```{r}
fit_full=glm(formula = survival ~ factor(gender)+factor(occupation), data = clean.data, family = binomial(link = logit))
summary(fit_full)

```

- Among all medical occupations, females are more likely to die from the infection of Covid19 according to the data.

- Among all medical occupations, the estimated conditional odds ratio between the death of Covid19 and gender is $\exp(`r round(fit_full$coefficients[2], 2)`)= `r round(exp(fit_full$coefficients[2]), 2)`$. 

- Among male medical works, the estimated odds of death of Covid19  is just $`r round(exp(fit_full$coefficients[2]), 2)*100`\%$ of that in female ones.

  

- Among both genders of infected medical workers, nurses are more likely to die than physicians and other medical staffs.

- Among a specific gender, the estimated odds that physicians die from Covid19 infection is $\exp(`r round(fit_full$coefficients[4], 2)`)= `r round(exp(fit_full$coefficients[4]), 2)`$ times the estimated odds for nurses.

- Among a specific gender, the estimated odds that other medical staffs die from Covid19 infection is $\exp(`r round(fit_full$coefficients[3], 2)`)= `r round(exp(fit_full$coefficients[3]), 2)`$ times the estimated odds for nurses.


## Analysis of Infected Cases through General Linear Model 

```{r}
count.data=clean.data %>% count(gender, occupation, province)

fit_infected=glm(formula = n ~ factor(gender) + factor(occupation)+factor(province), data = count.data, family = poisson)
summary(fit_infected)
```

- According to the data, male medical works are slightly more likely to be infected by Covid19.
- In each category of occupation and location, the number of infected male medical workers is $\exp(-0.88)=0.41$ more than that of females.
- Nurses are slightly less likely to be infected by Covid19 than physicians and other medical staffs.
- Among both genders, there are $\exp(-0.42)=0.66$  more physicians infected than nurses. 
- There are $\exp(-1.05)=0.35$ more other medical staffs infected than nurses.

- In Hubei province, medical workers are more likely to be infected. 
- There are $\exp(5.72)=305$ more medical workers infected in Hubei than in other provinces.
