---
title: "Example of Analysis"
author: "Panfeng Liang"
date: "June 22, 2020"
output:
  pdf_document: default
  
font-size: 14pt
---

```{r include=FALSE}
#library(readxl)
#library(ggplot2)
library(dplyr)
clean.data=read.csv("data.csv")
attach(clean.data)
```



## Analysis on the Number of Infected Cases through Log Linear Model 

```{r}
count.data=clean.data %>% count(gender, occupation, province)

fit_infected=glm(formula = n ~ factor(gender) + factor(occupation)+factor(province), 
                 data = count.data, family = poisson(link=log))
summary(fit_infected)
```
****************************************

**According to the data, female medical works are more likely to be infected by Covid19.**

- In each category of occupation and location, the number of infected male medical workers is $\exp(`r round(fit_infected$coefficients[2], 2)`)= `r round(exp(fit_infected$coefficients[2]), 2)`$ that of females.

**Nurses are more likely to be infected by Covid19 than physicians and other medical staffs.**

- Among both genders, physicians infected by Covid19 is just $\exp(`r round(fit_infected$coefficients[4], 2)`)= `r round(exp(fit_infected$coefficients[4]), 2)`$ times that of nurses. 
- Among both genders, other medical staffs infected by Covid19 is just $\exp(`r round(fit_infected$coefficients[3], 2)`)= `r round(exp(fit_infected$coefficients[3]), 2)`$ times that of nurses. 

**In Hubei province, medical workers are more likely to be infected.**

- Medical workers infected in other provinced are just $\exp(`r round(fit_infected$coefficients[5], 2)`)= `r round(exp(fit_infected$coefficients[5]), 2)`$ of that in Hubei provinces.


## Analysis on the Death Rate through Logistic Model :

```{r}
fit_death=glm(formula = survival ~ factor(gender)+factor(occupation), 
             data = clean.data, family = binomial(link = logit))
summary(fit_death)

```

********************************************
**Among all medical occupations, females are more likely to survive from the infection of Covid19 according to the data.**

- Among all medical occupations, the estimated conditional odds ratio between the survival of Covid19 and gender is $\exp(`r round(fit_death$coefficients[2], 2)`)= `r round(exp(fit_death$coefficients[2]), 2)`$. 

- Among male medical works, the estimated odds of survival of Covid19 infection is just $`r round(exp(fit_death$coefficients[2]), 2)*100`\%$ of that in female ones.

  

**Among both genders of infected medical workers, nurses are more likely to survive than physicians and other medical staffs.**

- Among a specific gender, the estimated odds that physicians survive from Covid19 infection is $\exp(`r round(fit_death$coefficients[4], 2)`)= `r round(exp(fit_death$coefficients[4]), 2)`$ times the estimated odds for nurses.

- Among a specific gender, the estimated odds that other medical staffs survive from Covid19 infection is $\exp(`r round(fit_death$coefficients[3], 2)`)= `r round(exp(fit_death$coefficients[3]), 2)`$ times the estimated odds for nurses.
